---
title: "Example_Data_Model"
author: "Andrew Thornton"
date: "2024-07-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Model

Using a separate data model allows us to abstract the processing of the data to ensure that everyone is using/cleaning the data in the same mannner.  If there's a mistake with this approach, then we only have to fix it in one spot. You load the data model in a similar method to how you load libraries, by including this at the top of your script.  Make sure your script is being run in the same directory as the data_model.R file as well as your source data file.  

``` {r}
source('data_model.R')
```

This simple data model currently supports 4 types of returned datasets, detailed below with an example:

## get_data() - this is simply our source data with StudentID and GPA removed.  

```{r}
df_simple = get_data()
head(df_simple)
```

## get_data_scaled() - this is our data set, except we are scaling all of the independent variables.  GradeClass remains as provided.

```{r}
df_scaled = get_data_scaled()
head(df_scaled)
```

## get_data_with_success() - this is our data set, except we are removing the provided 'GradeClass' column and replacing it with a new 'Success' column.  'Success' will be true when GradeClass = 0,1 and that is already determined for you within the datamodel.  This data is NOT scaled.

```{r}
df_success = get_data_with_success()
head(df_success)
```

## get_data_scaled_with_success() - this is our data set both scaled and with the Success column added, using the data definitions above.

```{r}
df_scaled_success = get_data_scaled_with_success()
head(df_scaled_success)
```