---
title: "KNN Analysis"
author: "Andrew Thornton"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stargazer)
library(class)
source("functions.r")
```

```{r set up, echo=TRUE}
Performance <- read.csv("Student_performance_data _.csv")
```

# Classification Models

## K-Nearest Neighbor, trying to classify success (gradeclass = 0,1) through the independent variables in the dataset
PART I: Prepping Data by defining a success as well as removing the fields we don't need
``` {r}
df = Performance
df$Success = ifelse(df$GradeClass < 2, 1, 0)
df$StudentID = NULL
df$GPA = NULL
df$GradeClass = NULL
```

PART II: Normalizing the data, finding index of our success column and breaking the data into 3 subsets
``` {r}
df[,1:12] = scale(df[,1:12])
col_index = which(colnames(df) == 'Success')
df_sets = subset_data(df, .6)

dftrain = data.frame(df_sets[1])
dfvalidation = data.frame(df_sets[2])
dftest = data.frame(df_sets[3])
```

PART III: KNN Classification Models - finding best k then calculating error and RMSE for validation and test
``` {r}
kmax = 20
bestK = best_k(kmax, dftrain, dfvalidation, dftest, col_index)

pred.train <- knn(dftrain[,-col_index], dftrain[,-col_index],dftrain[,col_index], k=bestK)
pred.val <- knn(dftrain[,-col_index], dfvalidation[,-col_index],dftrain[,col_index], k=bestK)
pred.test <- knn(dftrain[,-col_index], dftest[,-col_index],dftrain[,col_index], k=bestK)

(val.error = calculate_error_rate(dfvalidation, pred.val, col_index ))
(test.error = calculate_error_rate(dftest, pred.test, col_index))

#RMSE isn't accurate yet - have to adjust the functions file
(val.rmse = calculate_r